Finite-state morphological transducers for three Kypchak languages

### 2013-10-20 kipchak-lrec-2013/kipchak-paper.tex
a little work
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@48154 72bbbca6-d526-0410-a7d9-f06f51895060

\abstract{Hargle, bargle.\\
\Keywords{Kazakh, Tatar, Kumyk, morphology, transducer}}

@@

The Northwestern branch of Turkic is often referred to as the Kypchak branch, and can be divided into three subbranches.  Kumyk is a member of the Western Kypchak group, Tatar is a member of the Northern Kypchak group, and Kazakh is a member of the south Kypchak group \citep[82-83]{histofturkic}.  The geographic distribution of the languages is shown in map \ref{}.

@@

@@

\subsection{Kazakh}

\subsection{Tatar}

\subsection{Kumyk}

>>>>

\abstract{Hargle, bargle.\\
	\Keywords{Kazakh, Tatar, Kumyk, morphology, transducer}
}

@@

This paper describes the development of morphological transducers for three closly related languages: Kazakh, Tatar, and Kumyk.

These languages belong to the Northwestern branch of Turkic, which is often referred to as the Kypchak branch.  This branch can be divided into three subbranches.  Kumyk is a member of the Western Kypchak group, Tatar is a member of the Northern Kypchak group, and Kazakh is a member of the Southern Kypchak group \citep[82-83]{histofturkic}.  As such, each of these three languages represents a different one of the three branches of Kypchak.  The geographic distribution of the languages is shown in map \ref{}.

In a linguistic sense, these languages have different amounts of influence from other Turkic branches (e.g., moderate Oguz (SE) influence in the Western group, slight Oguz influence in the Northern group) and from Mongolic languages (moderate influence on the Southern group, lighter in the other groups), and all have heavy influence from Persian.

@@

%FIXME: background on how, when, and with what support were developed?
The transducers for these languages

@@

\subsection{Kazakh}
Kazakh has approximately 12 million speakers

\subsection{Tatar}
Tatar has approximately  million speakers

\subsection{Kumyk}
Kumyk has approximately  million speakers
